Portable Development Methodology

### 2024-02-05 latex/ms.tex
.

\documentclass[journal]{IEEEtran}
\usepackage{dirtree}
\usepackage[boxed]{algorithm2e}
\usepackage[nopdftrailerid=true]{pdfprivacy}

@@

Use cases of the Makefile include:
\begin{itemize}
	\item regression testing and debugging, to ensure that changes to \texttt{code} do not alter the \texttt{artifacts},
	\item portable development environment across multiple \texttt{developers},
	\item portable development environment across time.
\end{itemize}

Makes use of pre-existing standards:
\begin{itemize}
	\item GNU standard targets for Makefile~\cite{stallman1992gnu}
	\item POSIX Utilities and Shell~\cite{lewine1991posix}
\end{itemize}

We use Makefile to create the isolated environment (container) by creating all required files if not already present and to make sure that subsequent changes to the requirements update the environment.

The interface of the Makefile is a subset of the GNU standard targets:
\begin{verbatim}
make           # execute code 
make STAGING=1 # execute staging code 
make check     # check code
make clean     # remove tmp/
\end{verbatim}

With the \texttt{STAGING} environment variable which can be used for debugging purposes and having fast development iteration.

\section{Folder structure}
\dirtree{%
.0 python.
.1 \texttt{.dockerignore}.
.1 \texttt{.gitignore}.
.1 Dockerfile.
.1 Makefile.
.1 main.py.
.1 prm/.
.1 pyproject.toml.
.1 tmp/.
}

>>>>

\documentclass[journal]{IEEEtran}
\usepackage[boxed]{algorithm2e}
\usepackage[nopdftrailerid=true]{pdfprivacy}

@@

Use cases of the Makefile include:
\begin{itemize}
	\item regression testing and debugging, to ensure that changes to \texttt{code} do not alter the generated data,
	\item portable development environment across multiple \texttt{developers},
	\item portable development environment across time.
\end{itemize}

\section{Directory structure}
The following directory structure is the superset of files and directories that the \texttt{python/} directory can consist.
The interface of the Makefile is a subset of the GNU standard targets:
\begin{itemize}
	\item \texttt{.dockerignore}: Consists of:
		\begin{itemize}
			\item * (every file/directory)
			\item except files needed for environment creation (e.g.\ \texttt{pyproject.toml})
		\end{itemize}
	\item \texttt{.gitignore}: Consists of:
		\begin{itemize}
			\item the temporary directory \texttt{tmp/} and
			\item the environmental variable file \texttt{.env}.
		\end{itemize}
	\item \texttt{Dockerfile}: Rarely editable. The developer edits:
		\begin{itemize}
			\item the FROM image and
			\item whether other apt-get installations are done.
		\end{itemize}
	\item \texttt{Makefile}: Non-editable. Properties~\cite{stallman1992gnu}:
		\begin{itemize}
			\item It should be POSIX-compliant and use POSIX utilities~\cite{lewine1991posix}.
			\item The \texttt{all} target should generate data saved in \texttt{tmp/}.
			\item The \texttt{check} target should check all \texttt{code}. It should also check and disallow any additional files or directories besides the ones defined here.
			\item The \texttt{clean} target should delete \texttt{tmp/}.
			\item It should support a \texttt{STAGING} environment variable which can be used for debugging purposes and having fast development iteration.
			\item It should create all files and directories from the structure if they do not already exist.
		\end{itemize}
	\item \texttt{main.py}: Frequently editable. The developer writes \texttt{code} in here that generates data saved in \texttt{tmp/}.
	\item \texttt{prm/}: The developer can place here all the files/directories for which generation from code is infeasible. This should be as small as possible.
	\item \texttt{pyproject.toml}: Rarely editable. The developer edits:
		\begin{itemize}
			\item the dependencies and
			\item the version of the dependencies
		\end{itemize}
	\item \texttt{tmp/}: Data generated by \texttt{main.py} are saved here.
\end{itemize}
